\begin{thebibliography}{7}

\bibitem{Carlson} Carlson D.A., Haurie A.B., Leizarowitz A. Infinite horizon optimal control. Deterministic and stochastic systems. Berlin: Springer, 1991.

\bibitem{Halkin} Halkin H. Necessary conditions for optimal control problems with infinite horizons // Econometrica. 1974. V. 42. P. 267–272.

\bibitem{Helbig} A. Helbig, O. Abel, W. Marquardt, Structural concepts for optimization based control of transient processes, in: F. Allgower, A. Zheng (Eds.), Nonlinear Model Predictive Control, volume 26 of Progress in Systems and Control Theory, Birkhauser, Basel, 2000, pp. 295–311.

\bibitem{Houska} B. Houska, H. Ferreau, and M. Diehl, An Auto-Generated Real-TimeIteration Algorithm for Nonlinear MPC in the Microsecond Range, Automatica, vol. 47, no. 10, pp. 2279–2285, 2011.

\bibitem{Keerthi} Keerthi S. S., Gilbert E. G. Optimal infinite-horizon feedback laws for a general class of constrained discrete-time systems: Stability and moving-horizon approximations //Journal of optimization theory and applications. – 1988. – Т. 57. – №. 2. – С. 265-293.

\bibitem{Marlin} T.E. Marlin, A.N. Hrymak, Real-time operations optimization of continuous processes, in: Proceedings of the Fifth International Conference on Chemical Process Control, Tahoe City, CA, 1996, P. 156–164.

\bibitem{QUIN} Quin S.J., Badgwell T.A., Survey of industrial model predictive control technology, Science Direct //Control Engineering Practice, Elsevier Science., Austin, TX, USA. – 2002.

\bibitem{Ramsey} Ramsey F.P. A mathematical theory of saving // Econ. J. 1928. V. 38. P. 543–559

\bibitem{Shell} Shell K. Applications of Pontryagin’s maximum principle to economics // Mathematical systems theory and economics 1. Berlin: Springer, 1969. P. 241–292.

\bibitem{Kryazhimski} Асеев С. М., Кряжимский А. В. Принцип максимума Понтрягина и задачи оптимального экономического роста //Труды Математического института имени В.А. Стеклова. – 2007. – Т. 257, №. 10. – С. 3-271.

\bibitem{Diplom} Вдовенко Е.С. Оптимизация модели открытой экономики с ограничением на международное заимствование / Е.С Вдовенко // Диплом Белорусского государственного университета, Минск, 2017

\bibitem{Tihomirov} Иоффе А.Д., Тихомиров В.М. Теория экстремальных задач. М.: Наука, 1974.

\bibitem{differential} Мышенков В.И., Мышенков Е.В. Численные методы. Ч. 2. Численное решение обыкновенных дифференциальных уравнений: Наука, 2005. 

\bibitem{Pontragin} Понтрягин Л.С., Болтянский В.Г., Гамкрелидзе Р.В., Мищенко Е.Ф. Математическая теория оптимальных процессов. М.: Физматгиз, 1961.

\bibitem{Philipov} Филиппов А.Ф. О некоторых вопросах теории оптимального регулирования // Вестн. Моск. ун-та. Сер. мат., мех., астрон., физ., хим. 1959. №2. С. 25–32.

\end{thebibliography}
 